Using \LaTeX\ to submit manuscripts to peer reviewed journals.

### 2014-03-05 docs/thesis/chap-evaluation.tex
typo quality resukts

\section{Quality resukts}
In this section we are interested in evaluating the quality of the results provided by our system.
The type of queries that $5e^{x+y}$ was designed for, are typical equations that can be found in a physics scientific publication. 
Out main user case is that a user of CDS is interested in finding documents inside the collection whose equations are related to the one that is provided.

@@

@@

%%
%\begin{longtable}{|m{3.5cm}|>
%{\centering\arraybackslash}m{3cm}|>
%{\centering\arraybackslash}m{3cm}|>
%{\centering\arraybackslash}m{5cm}|
%}
%\hline 
%\textbf{\LaTeX} & 
%\textbf{Presentation MathML} & 
%\textbf{Content MathML + Presentation Markups} & 
%\textbf{OpenMath}  \\ \hline
%%%

>>>>

\section{Quality results}
In this section we are interested in evaluating the quality of the results provided by our system.
The type of queries that $5e^{x+y}$ was designed for, are typical equations that can be found in a physics scientific publication. 
Out main user case is that a user of CDS is interested in finding documents inside the collection whose equations are related to the one that is provided.

@@

We also were interested in also using the Fully Simplify function in Mathematica but we found no difference between both forms and the results were the same.

@@
